### 2014-05-20 tex/main-body-text.tex

The allocation of indivividuals into K clusters is congruent for each program. For all six groups 
of runs from \textit{k}=2-4, {\sc flock} lead to nearly identical clustering of individuals 
(See supplementary materials). It should be noted
that of the 50 starting allocations of individuals in the {\sc flock} procedure only the LLOD for the 
 'best run' is reported. Of these 'best runs' for a \textit{k} of 2 only two  
ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As \textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

Despite the similar allocation of individuals into \textit{k} clusters, the 
plateau analysis in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from both the pure likelihood 
and delta K approach in {\sc structure}. While no plateaus were observed in any of the six groups 
for a \textit{k} $\geq$2, the plateau record varied greatly among each
 group for \textit{k}=2 (plateau  sequences- Run1= 3,2,3,7,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; 
Run4=2,3,4,2,4,3; Run5=2,2,5,5,3; and; Run6=2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of K$\geq$2 (Run1) or \textit{undecided} as a consequence of no plateau 
lengths being greater than 6. Interpreting the results from {\sc structure} can either be done 
with the estimated likelihood of the data from the program itself or by the delta k method 
suggest by Evanno et al XXXXX. Both methods indicate that the most likely \textit{k} for the dataset is 6.

@@

\section*{Conclusions}
The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space for any given k can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind. The results of {\sc flock} depend primarily on the initial partition of 
individuals. It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters. It is difficult to 
access how well the reallocation process moves the cluster of individuals within the 
partition space due to the fact that the reallocation matrix from only the 'best-run' 
is reported.

>>>>

The allocation of indivividuals into K clusters was congruent for each program. For all six groups 
of runs from \textit{k}=2-4, {\sc flock} lead to nearly identical clustering of individuals 
(See supplementary materials). It should be noted
that of the 50 starting allocations of individuals in the {\sc flock} procedure likelihoods of each individual in 
each reference is only reported for the 
 'best run'. Of these 'best runs' for a \textit{k} of 2 only two  
ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As \textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

Despite the similar allocation of individuals into \textit{k} clusters, the 
plateau analysis in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from {\sc structure}. While no plateaus were observed in any of the six groups 
for a \textit{k} $\geq$2, the plateau record varied greatly among each
 group for \textit{k}=2 (plateau  sequences- Run1= 3,2,3,7,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; 
Run4=2,3,4,2,4,3; Run5=2,2,5,5,3; and; Run6=2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of K$\geq$2 (Run1) or \textit{undecided} as a consequence of no plateau 
lengths being greater than 6. Interpreting the results from {\sc structure} is often accomplished by 
looking at the estimated log likelihood of the data given K, the delta k method \citep{Evannoetal2005}, and plots of 
individual \textit{$q_i$} values. Both the estimated likelihood of the data
and the plots of individuals \textit{$q_i$} values suggest that 
the most likely \textit{k} for the dataset is 6.

@@

\section*{Conclusions}

One of the major claimed advantages of {\sc flock} over MCMC methods for solving the 
K-partition problem is that, '[t]he very short processing times for each run of {\sc flock} allows for
 comparing partitions from many runs of each \textit{k}'' \citep[][p.~735]{Duc&Tur2012}.
While the authors observed improved process time in their 
comparisions we did not observe the same advantage in our analysis. In their comparison, the 
run parameters for {\sc flock} were 50 runs and 20 iterations for each \textit{k} = 1 to K+4. 
These process times were compared to the admixture model with correlated allele 
frequencies in {\sc structure} with ten iterations of a 50,000 sweep burn-in followed 
by 200,000 sweep sample from the posterior of \textit{k} from 1 to K+3. 
It seems reasonable, for each \textit{k}, to compare one iteration of {\sc structure} 
to one iteration of {\sc flock} with 50 different starting allocations that are reallocated 20 times 
as both evaluate the partition space once. Process speed advantages also may only been observed 
with low sample sizes. The authors evaluated simulated data sets with sample sizes of N = 60, 120, 
and 240.

The partition space over which {\sc flock} evaluates how individuals are clustered 
greatly increases with both the number of individuals and the number of clusters into 
which they can be partitioned. The total partition space for any given k can be 
defined by $\sum\limits_{i=1}^k S(n,k)$ where S(n,k) is a Stirling number of the 
second kind. The results of {\sc flock} depend primarily on the initial partition of 
individuals. It is not surprising that with 2,596 individuals we could have 
drastically different plateau sequences with just two clusters and that as \textit{k} increases
{\sc flock} finds suboptimal allocations.

For those that do decide to use {\sc flock} as an alternative to {\sc structure}, the adhoc rules 
to estimate K may be overly stringent. While there has been ample 
discourse concering choosing the optimal K in  {\sc structure} \citep{Evannoetal2005, 
Pricharedetal2000, Wap&Gag2006} and \citet{Pritchardetal2000} urges users 
to be cautious of interpreting K, no such care in interpreting results 
is suggested in running {\sc flock}. The authors developed estimation rules based on simulated data 
sets with different migration regimes and rates, number of loci, and K. 
By relying on identical allocations (mean LLOD values) as a means of supporting 
a particular \textit{k},  similar but not idential 
allocations will provide no support to a given \textit{k}. This may not be as big an issue with small datasets,
however, as sample sizes increase this could have a drastic influence on the estimation of 
K.
